Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-10 paper/paper.tex
microtype
line break

\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb,amsmath,amsfonts} 
\usepackage{mathtools}

@@

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behavior whereas the controller operates in
discrete time and over a quantized domain.  Inspired by a classical approach
\cite{astrom1997computer}, we translate the problem into a single digital
domain.  Given our primary interest in stability despite digitization
effects, we have modeled a digital equivalent of the plant by evaluating the
effects of the quantizers (A/D and D/A converters) as time discretization
elements with quantization noise.  The resulting closed-loop system is a
program loop that operates on bit-vectors encoded using fixed-point
arithmetic with finite word length (FWL).  The deterministic effects of the
FWL and quantization errors are incorporated into the model as an additive
uncertainty, which is taken into account during the CEGIS-based synthesis of
the control software for the plant.

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most work in verification focusses on finding a correct
variant of a known controller, e.g., by looking for optimal parameter
representations using FWL, but ignore the effects of rounding errors due to
issues of mathematical tractability.  The analyses
in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.  If the error of the
implementation is lower than this tolerance level, then the verification is
successful.

>>>>

\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb,amsmath,amsfonts} 
\usepackage{mathtools}
\usepackage{microtype}

@@

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behavior whereas the controller operates in
discrete time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  Given our primary interest in stability despite
digitization effects, we have modeled a digital equivalent of the plant by
evaluating the effects of the quantizers (A/D and D/A converters) as time
discretization elements with quantization noise.  The resulting closed-loop
system is a program loop that operates on bit-vectors encoded using
fixed-point arithmetic with finite word length (FWL).  The deterministic
effects of the FWL and quantization errors are incorporated into the model
as an additive uncertainty, which is taken into account during the
CEGIS-based synthesis of the control software for the plant.

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most work in verification focusses on finding a correct
variant of a known controller, e.g., by looking for optimal parameter
representations using FWL, but ignore the effects of rounding errors due to
issues of mathematical tractability.  The analyses
in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.  If~the error of the
implementation is lower than this tolerance level, then the verification is
successful.
